### 2022-04-25 ch1.tex
final committee revisions

Computational social science and social science disciplines are quick to adopt
new sources of digital trace data for use in academic research. In this article,
I examine the criterion validity of one of these new sources, Google Search
Trends. I validate how Google Trends can be used to demonstrate three different
cases, namely attitudes, disease prevalence and political preferences using five
different validated data sources. This paper asks, ``How can we operationalize
Google Search Trends as a valid indicator for uses in social science research?''
I use Pearson and Repeated Measures Correlations between the Google Trends and
the validated indicators as well as multiple linear regression (for
cross-sectional datasets) and fixed effect hierarchical linear models (for
longitudinal datasets) as additional tests of the data.

I find no correlation among any of the Google Trends tested and their validated
indicators. While some Google Trends tested were significantly associated with
the outcome in the regression models, effects tended to be small and the total
model interpretability remained low, even when controlling for demographic
variables. This article shows that there is no external or criterion validity of
Google Trends for these uses and social scientists will find no replacement for
high quality survey data with Google Trends. Instead, we must only use Google
Trends to demonstrate interest or attention.

>>>>

Computational social science and social science disciplines are quick to adopt
new sources of digital trace data for use in academic research. In this article,
I examine the criterion validity of one of these new sources, Google Search
Trends. Criterion validity looks at how well an operationalization of a specific
construct is able to predict a theoretical representation of the construct — the criterion.
I validate how Google Trends can be used as an operationalization of three different
cases, namely attitudes, disease prevalence and political preferences using five
different validated data sources. This paper asks, ``How can we operationalize
Google Search Trends as a valid indicator for uses in social science research?''
I use Pearson and Repeated Measures Correlations between the Google Trends and
the validated indicators as well as multiple linear regression (for
cross-sectional datasets) and fixed effect hierarchical linear models (for
longitudinal datasets) as additional tests of the data.

I find no correlation among any of the Google Trends tested and their validated
indicators. While some Google Trends tested were significantly associated with
the outcome in the regression models, effects tended to be small and the total
model interpretability remained low, even when controlling for demographic
variables. This article shows that there is no criterion validity of
Google Trends for these uses and social scientists will find no replacement for
high quality survey data with Google Trends. Instead, we must only use Google
Trends to demonstrate interest or attention.

### 2022-04-25 paper1.tex
final committee revisions

I will use three categorizations of ways I propose Google Trends could be
utilized for social scientific usage. First, I test Google Trends as an
indicator of attitudinal indicators. After
\citet{bailCulturalEnvironmentMeasuring2014}'s call for cultural sociologists to
utilize the ever-expanding world of big data, Google Trends began slowly
appearing as a data source in sociological and social science research. From
research on mass shootings and firearms
\citep{brownsteinInternetSearchPatterns2020, semenzaInformationseekingWakeTragedy2020},
protest and anti-Muslim sentiment
\citep{bailUsingInternetSearch2018,barrieSearchingRacismGeorge2020,grossThereFergusonEffect2017},
to analyzing country-level changes in social perception \citep{reyes_etal18},
Google search trends are a new and innovative indicator of cultural interest.
Extending into social networks and culture,
\citet{bailPrestigeProximityPrejudice2019} even used Google trends to measure
how they saw 'culture' spreads around the globe through the proliferation of
search terms.

@@

\subsubsection{Google Trends}
This paper focuses on a triangulation of Google search trends
\citep{googletrends} with other sources of credible data. Google trends portray
the search frequency for specific search terms across designated media markets
areas (DMAs), a nonoverlapping aggregation of U.S. counties to 210 media markets
based on Nielsen's classification of ``similar population clusters''
\citep{dma_key}. Raw data is on a scale from zero to one hundred, with one
hundred being the maximum search popularity out of all DMAs. When available, I
use Google search topics to measure trends as opposed to search terms. Search
topics are a more robust measurement than a single search term: topics are
aggregations of the rates of multiple, highly correlated search terms together
into a cohesive topic done by Google through it's Knowledge Graph product. For
example, while 'Beyoncé', 'Beyonce' and 'beyonce knowles' are all separate
search terms, 'Beyoncé Knowles' encompasses all of these into a single search
topic. Google Search Trends are only available cross-sectionally (a single
period across a geography) or as time-series (a single geo-location across
time). To remedy this and build a longitudinal dataset of each search topic to
match the longitudinal validated measures, I follow the method proposed in
\citet[][p. 5]{park_etal}\footnote{This method involves building a dataset of
unscaled cross-sectional values, selecting a DMA to use to establish the
rescaling ratio (I use 'Los Angeles CA'), and then finding the time-series
values for the one DMA. To find the rescaling ratio for each week in the
time-series, you divide the time-series value for each week by the
cross-sectional value for each week, resulting in a rescaling vector to be used
for all weeks in the dataset across geographies. To rescale each longitudinal
value, multiply the respective week's rescaling ratio by the cross-sectional
value. To validate this method, I compared the rescaled longitudinal data
against multiple samples of time-series data. For a more in-depth explanation of
this procedure, see \citet[p. 5]{park_etal}}. I interpolate missing data points
in the longitudinal datasets using The Zoo package for R \citep{zoo} which estimates
the values of missing data points based on the immediately preceding and succeeding
time points for each separate time-series group. This differs from multiple imputation, 
which would take other features into account when estimating the missing data point.

@@

As an additional criteria to evaluate the strength of the relationships, I
employ multiple linear regression (for cross-sectional datasets) and fixed
effect hierarchical linear models \citep{pinheiro_etal21} (for longitudinal
datasets) to identify the strength of relationships across locales. Multiple
linear regression is appropriate because the cross-sectional data are non-nested
with a continuous outcome. Hierarchical linear models are necessary to control
for the between-subject variation in the longitudinal models. Fixed models are
appropriate because they extract the between group-differences from the model to
allow the reader to focus on the overall effects of each variable. In these
models, include location metadata like county population size, broadband rates,
and median income to adjust for potentially confounded relationships between
Google search Trends and credible indicators. 'County level fips mean' is included
in each model to control for within-group variation of the outcome, a standard practice
in mixed effects modeling. Identifying these possible
confounded relationships may help to explain why some articles find
relationships between the trends and outcomes while others did not. For linear
regression models, I normalize independent variables so that each variable
across each model is on the same scale and can be compared. In other words,
variables have been centered and scaled to have a mean of zero and standard
deviation of one. Results of these models are in Tables
\ref{tab:vacc_hes_analysis} through \ref{tab:pres_2020_analysis}. 
In addition to coefficients, each table include the marginal $R^2$ and sometimes 
a conditional $R^2$, the first describes the proportion of variance explained by the fixed factor alone and the latter the fixed and random factors.

@@

In addition to attitudinal measures, I attempt to validate Google Trends for
uses in the measurements of health indicators. The first indicator I assess is
COVID-19 case rates from 2020 through 2021. The Pearson correlation results
indicate negligible to weak relationships between the search terms and the
actual case rates across time and place. The repeated measures correlation
coefficient, a more reliable and less biased measure for longitudinal
correlations, reveals similarly weak results with a maximum correlation of 0.32
between 'smell loss' and rates of COVID-19. To further investigate the
relationship, I include the three trends in fixed effect hierarchical linear
models. Model 1 of Table \ref{tab:covid_analysis} indicates that the trends
themselves are able to explain about 20\% of the variation in COVID-19 rates
($r^2$ = 0.201). Few of the demographic variables influence COVID-19 rates in
models 2 or 3, though there is some suppression for median income, unemployment
rates, and population density. Model 3 has an $r^2$ of 0.200. I conclude that
the Google Trends are slightly related to COVID-19 rates, but that this
relationship is weak, and we should not attempt to use Google Trends as an
indicator of actual health outcomes.

@@

% # TODO All variables have been standardized, right? So when you say an effect is ``small,'' could you give an illustration? E.g., translate it back into metric coefficients? For example, ''for every 100 additional calls to a suicide hotline, the suicide rate increases by x per 1,000 residents, according to the model,'' or something like that?  The main thing is to have an intuitive description of what the effect size is, not just to look at a standardized coefficient of .002.

@@

% The sign in Model 1 is interesting. The more likely a voter is to vote against Clinton, the more they search for her? (Obsessive?) Is that right? Also, I may be not seeing this correctly, but again I think I'd be interested in an interpretation in the original metrics of variables: ''According to Model 1, for every 1,000 searches for Clinton, she received X% less of the total actual vote,'' or something like that.
In Table \ref{tab:pres_2016_analysis}, I outline the results for the model
predicting the county percentage of votes for Hillary Clinton. Model 1
demonstrates how well Google Trends predict the votes; while the trend for
'Hillary Clinton' is significantly associated with votes, the model's $r^2$
($r^2$ = 0.027) shows that it does little to help explain the model variance. On
the other hand, adding in demographic features improves the model fit quite
well, bringing the $r^2$ up to 0.313 in model 2 and $r^2$ 0.327 in model 3.
Table \ref{tab:pres_2020_analysis} shows this same analysis for the 2020
election and predicts the percentage of votes for Joe Biden. While this model is
analogous to those in Table \ref{tab:pres_2016_analysis}, this model 1
demonstrates how unrelated Google Trends can be from actual outcomes. In
conclusion, I find that Google Trends are an unreliable and invalid indicator of
political support.

@@

Some previous research has shown strong innovation in the computational social
sciences to gather sociodemographic data when survey or other research methods
are too costly \citep{blumenstockPredictingPovertyWealth2015}. Google Trends, in
theory, sounds like a promising data source to 'nowcast' attitudinal, health,
and political indicators. Not only would the data be easily and freely
accessible, but it would also provide indicators for areas where conducting
research may be too costly. The demand for this sort of indicator is clear and
fields like the health sciences have freely utilized this data source. However,
this article shows that Google Trends fails to map on to validated survey
metrics for attitudes, disease prevalence and political preferences. Social
scientists should not assume Google Trends data can serve as a replacement for
high quality survey data, at least for these measures.

>>>>

I will use three categorizations of ways I propose Google Trends could be
utilized for social scientific usage. First, I test Google Trends as an
indicator of attitudinal indicators. After
\citet{bailCulturalEnvironmentMeasuring2014}'s call for cultural sociologists to
utilize the ever-expanding world of big data, Google Trends began slowly
appearing as a data source in sociological and social science research. From
research on mass shootings and firearms
\citep{brownsteinInternetSearchPatterns2020, semenzaInformationseekingWakeTragedy2020},
protest and anti-Muslim sentiment
\citep{bailUsingInternetSearch2018,barrieSearchingRacismGeorge2020,grossThereFergusonEffect2017},
to analyzing country-level changes in social perception \citep{reyes_etal18},
Google search trends are a new and innovative indicator of cultural interest.
Extending into social networks and culture,
\citet{bailPrestigeProximityPrejudice2019} even used Google trends to measure
how they saw `culture' spreads around the globe through the proliferation of
search terms.

@@

\subsubsection{Google Trends}
This paper focuses on a triangulation of Google search trends
\citep{googletrends} with other sources of credible data. Google trends portray
the search frequency for specific search terms across designated media markets
areas (DMAs), a nonoverlapping aggregation of U.S. counties to 210 media markets
based on Nielsen's classification of ``similar population clusters''
\citep{dma_key}. Raw data is on a scale from zero to one hundred, with one
hundred being the maximum search popularity out of all DMAs. When available, I
use Google search topics to measure trends as opposed to search terms. Search
topics are a more robust measurement than a single search term: topics are
aggregations of the rates of multiple, highly correlated search terms together
into a cohesive topic done by Google through it's Knowledge Graph product. For
example, while `Beyoncé', `Beyonce' and `beyonce knowles' are all separate
search terms, `Beyoncé Knowles' encompasses all of these into a single search
topic. Google Search Trends are only available cross-sectionally (a single
period across a geography) or as time-series (a single geo-location across
time). To remedy this and build a longitudinal dataset of each search topic to
match the longitudinal validated measures, I follow the method proposed in
\citet[][p. 5]{park_etal}\footnote{This method involves building a dataset of
unscaled cross-sectional values, selecting a DMA to use to establish the
rescaling ratio (I use `Los Angeles CA'), and then finding the time-series
values for the one DMA. To find the rescaling ratio for each week in the
time-series, you divide the time-series value for each week by the
cross-sectional value for each week, resulting in a rescaling vector to be used
for all weeks in the dataset across geographies. To rescale each longitudinal
value, multiply the respective week's rescaling ratio by the cross-sectional
value. To validate this method, I compared the rescaled longitudinal data
against multiple samples of time-series data. For a more in-depth explanation of
this procedure, see \citet[p. 5]{park_etal}}. I interpolate missing data points
in the longitudinal datasets using The Zoo package for R \citep{zoo} which estimates
the values of missing data points based on the immediately preceding and succeeding
time points for each separate time-series group. This differs from multiple imputation, 
which would take other features into account when estimating the missing data point.

@@

As an additional criteria to evaluate the strength of the relationships, I
employ multiple linear regression (for cross-sectional datasets) and fixed
effect hierarchical linear models \citep{pinheiro_etal21} (for longitudinal
datasets) to identify the strength of relationships across locales. Multiple
linear regression is appropriate because the cross-sectional data are non-nested
with a continuous outcome. Hierarchical linear models are necessary to control
for the between-subject variation in the longitudinal models. Fixed models are
appropriate because they extract the between group-differences from the model to
allow the reader to focus on the overall effects of each variable. In these
models, include location metadata like county population size, broadband rates,
and median income to adjust for potentially confounded relationships between
Google search Trends and credible indicators. `County level fips mean' is included
in each model to control for within-group variation of the outcome, a standard practice
in mixed effects modeling. Identifying these possible
confounded relationships may help to explain why some articles find
relationships between the trends and outcomes while others did not. For linear
regression models, I normalize independent variables so that each variable
across each model is on the same scale and can be compared. In other words,
variables have been centered and scaled to have a mean of zero and standard
deviation of one. Results of these models are in Tables
\ref{tab:vacc_hes_analysis} through \ref{tab:pres_2020_analysis}. 
In addition to coefficients, each table include the marginal $R^2$ and sometimes 
a conditional $R^2$, the first describes the proportion of variance explained by the fixed factor alone and the latter the fixed and random factors.

@@

In addition to attitudinal measures, I attempt to validate Google Trends for
uses in the measurements of health indicators. The first indicator I assess is
COVID-19 case rates from 2020 through 2021. The Pearson correlation results
indicate negligible to weak relationships between the search terms and the
actual case rates across time and place. The repeated measures correlation
coefficient, a more reliable and less biased measure for longitudinal
correlations, reveals similarly weak results with a maximum correlation of 0.32
between `smell loss' and rates of COVID-19. To further investigate the
relationship, I include the three trends in fixed effect hierarchical linear
models. Model 1 of Table \ref{tab:covid_analysis} indicates that the trends
themselves are able to explain about 20\% of the variation in COVID-19 rates
($r^2$ = 0.201). Few of the demographic variables influence COVID-19 rates in
models 2 or 3, though there is some suppression for median income, unemployment
rates, and population density. Model 3 has an $r^2$ of 0.200. I conclude that
the Google Trends are slightly related to COVID-19 rates, but that this
relationship is weak, and we should not attempt to use Google Trends as an
indicator of actual health outcomes.

@@

% # TODO All variables have been standardized, right? So when you say an effect is ``small,'' could you give an illustration? E.g., translate it back into metric coefficients? For example, `'for every 100 additional calls to a suicide hotline, the suicide rate increases by x per 1,000 residents, according to the model,'' or something like that?  The main thing is to have an intuitive description of what the effect size is, not just to look at a standardized coefficient of .002.

@@

% The sign in Model 1 is interesting. The more likely a voter is to vote against Clinton, the more they search for her? (Obsessive?) Is that right? Also, I may be not seeing this correctly, but again I think I'd be interested in an interpretation in the original metrics of variables: `'According to Model 1, for every 1,000 searches for Clinton, she received X% less of the total actual vote,'' or something like that.
In Table \ref{tab:pres_2016_analysis}, I outline the results for the model
predicting the county percentage of votes for Hillary Clinton. Model 1
demonstrates how well Google Trends predict the votes; while the trend for
'Hillary Clinton' is significantly associated with votes, the model's $r^2$
($r^2$ = 0.027) shows that it does little to help explain the model variance. On
the other hand, adding in demographic features improves the model fit quite
well, bringing the $r^2$ up to 0.313 in model 2 and $r^2$ 0.327 in model 3.
Table \ref{tab:pres_2020_analysis} shows this same analysis for the 2020
election and predicts the percentage of votes for Joe Biden. While this model is
analogous to those in Table \ref{tab:pres_2016_analysis}, this model 1
demonstrates how unrelated Google Trends can be from actual outcomes. In
conclusion, I find that Google Trends are an unreliable and invalid indicator of
political support.

@@

Some previous research has shown strong innovation in the computational social
sciences to gather sociodemographic data when survey or other research methods
are too costly \citep{blumenstockPredictingPovertyWealth2015}. Google Trends, in
theory, sounds like a promising data source to `nowcast' attitudinal, health,
and political indicators. Not only would the data be easily and freely
accessible, but it would also provide indicators for areas where conducting
research may be too costly. The demand for this sort of indicator is clear and
fields like the health sciences have freely utilized this data source. However,
this article shows that Google Trends fails to map on to validated survey
metrics for attitudes, disease prevalence and political preferences. Social
scientists should not assume Google Trends data can serve as a replacement for
high quality survey data, at least for these measures.

### 2022-04-25 paper2.tex
final committee revisions

Information is all around us and permeates every facet of human society, from
the hordes of data gathered during the internet age or passing gossip between
friends. Human communication and human society are based on the circulation of
information and knowledge. Information can be shared by others through
information campaigns and consumed by an individual, called information push, or
intentionally sought out by individuals, called information pull
\citep{cybenkoFoundationsInformationPush1999}.

Information is especially important given the prominent trends of
misinformation, disinformation, and mistrust in traditional institutions
\citep{starbird19, kata10}. While no belief in false information can be thought
of as harmless \citep{douglas21} some discredited theories such as 'vaccines
cause autism' have major ramifications for both the individual and public
health. For example, a newfound public resistance to vaccination against Measles
by so-called 'anti-vaxxers' caused a 17\% increase in rates worldwide in 2019.
This increase killed  142,000 people, most of whom were children under the age
of five \citep{givetash19}. However, even in the ever-evolving research agenda
of misinformation and infodemiology \citep{eysenbach02}, much of the research
focuses on the 'push' or 'supply' side of information, like spaces where
individuals first encounter conspiracy theories or other information
\citep{johnsonOnlineCompetitionPro2020, broniatowski_etal20}.

@@

There are important factors that can influence information seeking strategies
besides the strength of social capital or ease of search. For instance, we can
borrow uses and gratifications theory (UGT) from studies of mass communication
\citep{blumlerUsesMassCommunications1974, tanMassCommunicationTheories1985}. UGT
posits that users are not passive consumers of media and that people have an
active role in choosing different sources of media based on their satisfaction
of specific needs on an individual basis. UGT is based on Maslow’s
\citeyear{maslowTheoryHumanMotivation1943} hierarchy of needs and is compatible
with Lazarsfeld and Katz’s theory of two-step flow
\citep{katzPersonalInfluencePart1955} because people can choose their media and
the opinion leaders they follow. Modern-day theorists have extended UGT theory
and classified the uses and gratifications of the internet and of social media.
\citet{staffordDeterminingUsesGratifications2004} theorize that the internet
provides gratification through useful content that meets expectations,
gratification from purposeful navigating or random browsing as a process, and
social gratification from forming and deepening social ties.
\citet{leungGenerationalDifferencesContent2013} theorizes that social media is
gratifying for users because it allows for venting of negative feelings,
provides recognition, provides entertainment, promotes social affection, and
fulfills cognitive needs.

@@

\begin{hyp}[H\ref{hyp:drgooglefriend}] \label{hyp:drgooglefriend}
Seeking information from experts, search engines, and other people
will be the most common modes of information search in comparison
to online forums and social networking sites. 
\end{hyp}

@@

Finally, in Table \ref{tab:table-model-3}, I investigate whether there is a
relationship between information receiving and information seeking behaviors and
the choice to get vaccinated against COVID-19 through a logistic regression
model predicting Vaccination Outlook. I find that receiving information from a
doctor or other medical profession is associated with 2.85 odds of choosing to
receive a COVID-19 vaccination (\emph{p} \textless{} 0.001) and that seeking
information from a doctor also increases the odds of vaccination by 4 (\emph{p}
\textless{} 0.001). I find that my respondents who received information on a
social networking site like Facebook or Twitter about the vaccines were 55\%
\textbf{less likely} to choose to get vaccinated than those who received no
information through that modality (\emph{p} \textless{} 0.001). However, I did
find that those who reached out to family or friends with their concerns were
77\% more likely to become vaccinated (\emph{p} \textless{} 0.05). Furthermore,
my respondents who held an Associate's degree or above had 3.6 higher odds of
becoming immunized (\emph{p} \textless{} 0.001). And finally, I found further
ethnoracial differences in my sample. I found that Hispanic-Latinos had 2.83
higher odds of vaccination than non-Hispanics (\emph{p} \textless{} 0.05) and
that my Asian sample had 4.73 higher odds as well over non-Asians (\emph{p}  =
0.09). See Figure \ref{fig:plot-model-3} for a visual representation of how
these different coefficients are related to vaccination outlook. 'Gender, Other'
is likely an outlier with an inflated effect here due to only 6 participants
being coded as 'Other' for their gender.

>>>>

Information is all around us and permeates every facet of human society, from
the hordes of data gathered during the internet age to passing gossip between
friends. Human communication and human society are based on the circulation of
information and knowledge. Information can be shared by others through
information campaigns and consumed by an individual, called information push, or
intentionally sought out by individuals, called information pull
\citep{cybenkoFoundationsInformationPush1999}.

Information push and pull are inherently tied to arguments of structure and agency.
That is, to what extent does the structure and institutions of society shape 
individual human behavior and to what extent do individuals actors control 
the decisions they make in the environment in which they find themselves. 
Attempts to reconcile the false dichotomy between structure and agency
are found among the majority of modern sociological theorists, particularly  
\citet{coleman1994foundations} and \citet{bourdieu1987distinction}.
Both renowned sociologists theorize how the external structures
are internalized by actors and inspire individual agency, which in turn 
can lead to an evolution of the external structures themselves.  
This article joins Coleman and Bourdieu in rejecting the false dichotomy
between structure and agency by investigating the complementary push (structure)  
and pull (agency) of information diffusion.

Information is especially important given the prominent trends of
misinformation, disinformation, and mistrust in traditional institutions
\citep{starbird19, kata10}. While no belief in false information can be thought
of as harmless \citep{douglas21} some discredited theories such as `vaccines
cause autism' have major ramifications for both the individual and public
health. For example, a newfound public resistance to vaccination against Measles
by so-called `anti-vaxxers' caused a 17\% increase in rates worldwide in 2019.
This increase killed  142,000 people, most of whom were children under the age
of five \citep{givetash19}. However, even in the ever-evolving research agenda
of misinformation and infodemiology \citep{eysenbach02}, much of the research
focuses on the `push' or `supply' side of information, like spaces where
individuals first encounter conspiracy theories or other information
\citep{johnsonOnlineCompetitionPro2020, broniatowski_etal20}.

@@

There are important factors that can influence information seeking strategies
besides the strength of social capital or ease of search. For instance, we can
borrow uses and gratifications theory (UGT) from studies of mass communication
\citep{blumlerUsesMassCommunications1974, tanMassCommunicationTheories1985}. UGT
posits that users are not passive consumers of media and that people have an
active role in choosing different sources of media based on their satisfaction
of specific needs on an individual basis. UGT is based on Maslow’s
\citeyear{maslowTheoryHumanMotivation1943} hierarchy of needs.
Modern-day theorists have extended UGT theory
and classified the uses and gratifications of the internet and of social media.
\citet{staffordDeterminingUsesGratifications2004} theorize that the internet
provides gratification through useful content that meets expectations,
gratification from purposeful navigating or random browsing as a process, and
social gratification from forming and deepening social ties.
\citet{leungGenerationalDifferencesContent2013} theorizes that social media is
gratifying for users because it allows for venting of negative feelings,
provides recognition, provides entertainment, promotes social affection, and
fulfills cognitive needs.

@@

\begin{hyp}[H\ref{hyp:drgooglefriend}] \label{hyp:drgooglefriend}
Seeking information from experts, search engines, and other people
will each be significantly more utilized modes of information search than seeking via 
online forums and social networking sites. 
\end{hyp}

@@

Finally, in Table \ref{tab:table-model-3}, I investigate whether there is a
relationship between information receiving and information seeking behaviors and
the choice to get vaccinated against COVID-19 through a logistic regression
model predicting Vaccination Outlook. I find that receiving information from a
doctor or other medical profession is associated with 2.85 odds of choosing to
receive a COVID-19 vaccination (\emph{p} \textless{} 0.001) and that seeking
information from a doctor also increases the odds of vaccination by 4 (\emph{p}
\textless{} 0.001). I find that my respondents who received information on a
social networking site like Facebook or Twitter about the vaccines were 55\%
\textbf{less likely} to choose to get vaccinated than those who received no
information through that modality (\emph{p} \textless{} 0.001). However, I did
find that those who reached out to family or friends with their concerns were
77\% more likely to become vaccinated (\emph{p} \textless{} 0.05). Furthermore,
my respondents who held an Associate's degree or above had 3.6 higher odds of
becoming immunized (\emph{p} \textless{} 0.001). And finally, I found further
ethnoracial differences in my sample. I found that Hispanic-Latinos had 2.83
higher odds of vaccination than non-Hispanics (\emph{p} \textless{} 0.05) and
that my Asian sample had 4.73 higher odds as well over non-Asians (\emph{p}  =
0.09). See Figure \ref{fig:plot-model-3} for a visual representation of how
these different coefficients are related to vaccination outlook. `Gender, Other'
is likely an outlier with an inflated effect here due to only 6 participants
being coded as `Other' for their gender.
